Neural Power Units

### 2020-06-05 papers/main.tex
rename plot for arxiv
arxiv branch

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
\usepackage{neurips_2020}

@@

\begin{abstract}
  Conventional Neural Networks can approximate simple arithmetic operations,
  but fail to generalize beyond the range of numbers that were seen during
  training.  \emph{Neural Arithmetic Units} aim to overcome this difficulty,
  but current arithmetic units are either limited to operate on positive
  numbers or can only represent a subset of arithmetic operations. We introduce
  the \emph{Neural Power Unit} (NPU) that operates on the \emph{full domain of
  real numbers} and is capable of \emph{learning arbitrary power functions} in
  a single layer.  The NPU thus fixes the shortcomings of existing arithmetic
  units and extends their expressivity. We achieve this by using
  complex arithmetic without requiring a conversion of the network to complex
  numbers. A simplification of the unit to the \emph{RealNPU} yields a highly interpretable model.
  We show that the NPUs outperform their competitors in terms of
  accuracy and sparsity on artificial arithmetic datasets, and that the RealNPU can discover
  the governing equations of a dynamical systems only from data.
\end{abstract}

@@

\begin{table}[h]
  \centering
  \caption{Testing error on the simple arithmetic task for the different models
  (i.e. mean of each heatmap in Fig.~\ref{fig:simple_err}). Each value is
  obtained by computing median (and median absolute deviation) of the error of
  20 models.}
  \label{tab:simple_err}
  \small
  \input{../plots/simple_err.tex}
\end{table}

>>>>

% to compile a preprint version, e.g., for submission to arXiv, add add the
% [preprint] option:
\usepackage[preprint]{neurips_2020}

@@

\begin{abstract}
  Conventional Neural Networks can approximate simple arithmetic operations,
  but fail to generalize beyond the range of numbers that were seen during
  training.  \emph{Neural Arithmetic Units} aim to overcome this difficulty,
  but current arithmetic units are either limited to operate on positive
  numbers or can only represent a subset of arithmetic operations. We introduce
  the \emph{Neural Power Unit} (NPU\footnote{Implementation of all used neural arithmetic units: \url{https://github.com/nmheim/NeuralArithmetic.jl} }) that operates on the \emph{full domain of
  real numbers} and is capable of \emph{learning arbitrary power functions} in
  a single layer.  The NPU thus fixes the shortcomings of existing arithmetic
  units and extends their expressivity. We achieve this by using
  complex arithmetic without requiring a conversion of the network to complex
  numbers. A simplification of the unit to the \emph{RealNPU} yields a highly interpretable model.
  We show that the NPUs outperform their competitors in terms of
  accuracy and sparsity on artificial arithmetic datasets, and that the RealNPU can discover
  the governing equations of a dynamical systems only from data.
\end{abstract}

@@

\begin{table}[h]
  \centering
  \caption{Testing error on the simple arithmetic task for the different models
  (i.e. mean of each heatmap in Fig.~\ref{fig:simple_err}). Each value is
  obtained by computing median (and median absolute deviation) of the error of
  20 models.}
  \label{tab:simple_err}
  \small
  \input{../plots/simple_err_table.tex}
\end{table}
